---
title: "Literacy in Tamil Nadu - Shiny project"
author: "Tinniam V Ganesh"
date: "Thursday, May 21, 2015"
output: html_document
---
# Executive summary
This project takes a look at the literacy in the state of Tamil Nadu in India. 
The project uses a Shiny UI and a Shiny Server. A simple radio button option is given to the 
user to check the details

#Details:
1. The UI portion of the Shiny app uses a simple radio button to chose options
2. Appropriate charts are displayed based on option chosen
3. Reactive output is shown in blue color

# UI code
```{r eval=FALSE}
shinyUI(
  pageWithSidebar(
    # Set the application title
    headerPanel("A look at literacy in the state of Tamil Nadu (India)"),
    
    # Set the radio buttons
    radioButtons("literacy", "Literacy in the state of Tamil Nadu (TN):",
                 c("Total Males & Females attending educational institutions in TN" = "a",
                   "Percent males  atending institutions in TN" = "b",
                   "Percent females attending institutions in TN " = "c",
                   "Pie chart for Tamil Nadu  of  persons  attending school" = "d")),
    
    # Create main panel
    mainPanel(
      
      # Add reactive text that changes when the user chooses an option
      tags$head(tags$style("#text1{color: blue;
                                 font-size: 16px;
                                 font-style: italic;
                           }"
      )
      ),
      # Reactive output
      textOutput("text1"),
      
      # Plot the output based on the user choice
      plotOutput(outputId = "main_plot", height = "300px")
    )
  )
)
```

# Server Code

```{r, eval=FALSE}
output$main_plot <- renderPlot({
  if (input$literacy == "a") {
    barplot(as.numeric(tnmat[6:7,]),names.arg=rep(tnmat[1,],each=2),main ="Persons attending educational institutions in TN - Males vs. Females", 
            xlab = "Age", ylab= "Number", col =c("red","darkblue"), legend= c("Males","Females"),beside=TRUE)   
  } else if (input$literacy == 'b') {
    #Calculate percent of males attending education of total
    percentM = round(as.numeric(eduM) *100/as.numeric(totalM),1)
    barplot(percentM,names.arg=tnmat[1,],main ="Percentage males attending educational institutions in TN ", 
            xlab = "Age", ylab= "Percentage", col ="lightblue", legend= c("Males")) 
  } else if (input$literacy == 'c') {
    #Calculate percent of females attending education of total
    percentF = round(as.numeric(eduF) *100/as.numeric(totalF),1)
    barplot(percentF,names.arg=tnmat[1,],main ="Percentage females attending educational institutions in TN ", 
            xlab = "Age", ylab= "Percentage", col ="lightblue", legend= c("Females")) 
    
  } else if (input$literacy == 'd') {
    #Pie chart for Tamil Nadu  of  persons between 15- 19 years attending school 
    slices <- c(tnmat[8,12],tnmat[11,12],tnmat[14,12],tnmat[17,12],tnmat[20,12])
    percentlabels <- round(as.numeric(slices) *100/as.numeric(tnmat[5,12],1))
    pielabels<- paste(percentlabels, "%", sep="")
    cols <- c("blue","green","cyan","red", "grey30")
    
    pie(as.numeric(slices), main="Tamil Nadu Literacy- Pie Chart", col=cols, labels=pielabels, cex=0.8)
    legend("topright", c("School","College","Vocational","Literacy center","Other"), cex=0.8, fill=cols)
  }
```

#Conclusion
1. The Shiny app uses a the radio button Widget
2. Charts are displayed based on user button
3. The Shiny app is kept simple and intuitive
4. Reactive output text is created based on user choice
